A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
wrote the device type section.

\subsubsection{Data Type}
Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}. Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information. Information which can be used to impersonate the user (i.e. username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data.

@@

\subsubsection{Device Type}

(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not. In either case, this matters the least, and device type and data recipient are more influencing factors. This is just the result of biases in people we can't quite quantify.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{device-type.png}
	\caption{(This is a placeholder! TODO: generate a better version of this)}
\end{figure}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c |}
 Question &  Wearable VUR & Smartphone VUR \\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.79\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

@@

Talk about results of between-subjects analysis here.

@@

there are too few instances where a participant got both, and therefore not enough data to really do analysis: Results of the effects of <device> type contributing to VUR. Values are McNeamar's test results for within-subjects comparisons for participants who received both questions.

@@

%I didn't do the correlation yet
(EXAMPLE) We found that the very upset rate for participants was not correlated with (pick correct ones from IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), positively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients), and negatively correlated with  (IUIPC, age, gender, education, wearable ownership) (give correlation coefficients).

Because wearable devices have been adopted by a younger, rich, technology-savvy demographic  \cite{cmo}, it is natural to see that younger or more educated participants have had a more favorable view of wearable devices. This may be due to cultural exposure through marketing or friends, or an attitude of openness to new technologies. Participants who had a higher IUIPC score, which infers a higher sensitivity to privacy, were more likely to be upset at the various scenarios which may occur when wearing a wearable device. Additionally, these people were more likely to be adverse to these technologies for the sake of preserving privacy, whether they had explicit concerns or a vague feeling of uneasiness. There was no correlation between a person's gender and their views of wearable devices, reaffirming that wearable devices are equally exposed to both genders.

@@

%should I just put the list in here, in the main part of the paper?

>>>>

\subsubsection{Data Type}
Irrespective with whom the data was shared or on what device, participants were most concerned about photos/videos, especially if they contain embarrassment, nudity, or financial information. Information which can be used to impersonate the user (i.e. username and password for websites) and invasions of privacy (photos of someone at home) were also considered to be sensitive data. Top and bottom absolute <data> rankings can be seen in Tables ~\ref{top10} and ~\ref{bottom10}. {\color{red} should I say anything about the full list of 74 data types?}

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 70.23\% VUR when asked about wearables devices and 40.62\% VUR when asked about smartphones.The VUR rates for both devices for all 5 quesions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c |}
 Question &  Wearable VUR & Smartphone VUR \\
 All & 70.23\% & 40.62\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.79\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

@@

@@

@@

@@

{\color{red} can you redo the graph for figure ~\ref{fig:techplot}? I trust your judgement on how it should look and what to emphasize.}
